Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks

### 2023-06-29 MasterThesis.tex
Updates from Overleaf

\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry} %Margins
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{chngcntr }
\usepackage[toc,page]{appendix}
\usepackage[T1]{fontenc}
\usepackage[nottoc]{tocbibind}
\usepackage[compact]{titlesec}
\usepackage{float}
\usepackage{booktabs}
\usepackage{makecell}

@@

%Title parameters
\title{%
  Uncovering underlying high-level musical content in the time domain \\
  \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to MIR downstream tasks}

\author{\href{oriol.colome.font@epidemicsound.com}{Oriol Colomé Font}}
\submitdate{July 2023}
\supervisor{Carlos Lordelo and Carl Thomé}
\cosupervisor{Frederic Font}

>>>>

\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry} %Margins
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{chngcntr }
\usepackage[toc,page]{appendix}
\usepackage[T1]{fontenc}
\usepackage[nottoc]{tocbibind}
\usepackage[compact]{titlesec}
\usepackage{float}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage{threeparttable}
\usepackage{adjustbox}

@@

%Title parameters
\title{%
  Uncovering underlying high-level musical content in the time domain \\
  \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks}

\author{\href{oriol.colome.font@epidemicsound.com}{Oriol Colomé Font}}
\submitdate{July 2023}
\supervisor{Carl Thomé and Carlos Lordelo}
\cosupervisor{Frederic Font}

### 2023-06-29 discussion/discussion.tex
Updates from Overleaf

While not outperforming state-of-the-art results or traditional audio features in contrast to research such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its outstanding performance in accuracy metrics and overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset). Most likely, so does for nearly all MIR downstream tasks that are not purely sonic-based.

@@

XXXXXX

>>>>

While not outperforming state-of-the-art results or traditional audio features in contrast to other research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its outstanding performance in accuracy metrics and overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset). Most likely, so does for nearly all MIR downstream tasks that are not purely sonic-based.

@@

While these do decode underlying high-level musical content effectively remain scientifically unanswered, the outstanding performance in precision metric

### 2023-06-29 results/results.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/first results.png}
    \caption{Caption}
    \label{fig:boxplotmetrics}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/f-measure.png}
    \caption{Caption}
    \label{fig:boxplotfmeasure}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/metrics.png}
    \caption[Metric comparison for different audio features. Boxplot]{Boxplot visual comparison of precision, recall, and f-measure for different features obtained using the SF algorithm \cite{sf} on the SALAMI dataset. Sliding windowed segments across the audio signal input signal is 4 seconds}
    \label{fig:boxplotmetrics}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/boudaryfscore.png}
    \caption[F-measure comparison for different audio features. Boxplot]{Boxplot visual comparison of f-measure for different features obtained using the SF algorithm \cite{sf} on the SALAMI dataset. Sliding windowed segments across the audio signal input signal is 4 seconds}
    \label{fig:boxplotfmeasure}
\end{figure}

### 2023-06-29 results/subsections/tables.tex
Updates from Overleaf

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|X|X|X|X|X|}
\hline
\textbf{Technique} & \textbf{Training Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\
\hline
MFCC & -- & 0.173 & 0.185 & 0.172 \\
\hline
Embeddiogram & GTZAN Dataset & 0.228 & 0.171 & 0.185 \\
\hline
Embeddiogram & MSD Dataset & \textbf{0.335} & 0.276 & 0.288 \\
\hline
PCP & -- & 0.311 & 0.324 & 0.305 \\
\hline
Tonnetz & -- & 0.312 & 0.312 & 0.300 \\
\hline
CQT & -- & 0.311 & \textbf{0.339} & \textbf{0.312} \\
\hline
\end{tabularx}
\caption[Metric comparison for different audio features]{Comparison of precision, recall, and f-measure for different features obtained using the SF algorithm \cite{sf} on the SALAMI dataset. Sliding windowed segments across the audio signal input signal is 4 seconds}
\label{tab:comparison}
\end{table}

>>>>

\newsavebox\mfccSF
\begin{lrbox}{\mfccSF}
\centering
   $\begin{aligned}
     0.173 & \quad 0.185 & \quad 0.172 % SF algorithm
    \end{aligned} $
\end{lrbox}

\newsavebox\mfccFoote
\begin{lrbox}{\mfccFoote}
\centering
   $\begin{aligned}
     ... & \quad ... & \quad ... % Foote algorithm
    \end{aligned} $
\end{lrbox}

\newsavebox\mfccCNMF
\begin{lrbox}{\mfccCNMF}
\centering
   $\begin{aligned}
     ... & \quad ... & \quad ... % CNMF algorithm
    \end{aligned} $
\end{lrbox}

\newsavebox\embeddioaSF
\begin{lrbox}{\embeddioaSF}
   $\begin{aligned}
     0.228 & \quad 0.171 & \quad 0.185
    \end{aligned} $
\end{lrbox}

\newsavebox\embeddioaFoote
\begin{lrbox}{\embeddioaFoote}
   $\begin{aligned}
     ... & \quad ... & \quad ...
    \end{aligned} $
\end{lrbox}

\newsavebox\embeddioaCNMF
\begin{lrbox}{\embeddioaCNMF}
   $\begin{aligned}
     ... & \quad ... & \quad ...
    \end{aligned} $
\end{lrbox}

\newsavebox\embeddiobSF
\begin{lrbox}{\embeddiobSF}
   $\begin{aligned}
     \textbf{0.333} & \quad 0.280 & \quad 0.288
    \end{aligned} $
\end{lrbox}

\newsavebox\embeddiobFoote
\begin{lrbox}{\embeddiobFoote}
   $\begin{aligned}
     0.275 & \quad \textbf{0.318} & \quad 0.280
    \end{aligned} $
\end{lrbox}

\newsavebox\embeddiobCNMF
\begin{lrbox}{\embeddiobCNMF}
   $\begin{aligned}
     0.248 & \quad 0.296 & \quad 0.254
    \end{aligned} $
\end{lrbox}

\newsavebox\pcpSF
\begin{lrbox}{\pcpSF}
   $\begin{aligned}
     0.311 & \quad 0.324 & \quad 0.305
    \end{aligned} $
\end{lrbox}

\newsavebox\pcpFoote
\begin{lrbox}{\pcpFoote}
   $\begin{aligned}
     ... & \quad ... & \quad ...
    \end{aligned} $
\end{lrbox}

\newsavebox\pcpCNMF
\begin{lrbox}{\pcpCNMF}
   $\begin{aligned}
     ... & \quad ... & \quad ...
    \end{aligned} $
\end{lrbox}

\newsavebox\tonnetzSF
\begin{lrbox}{\tonnetzSF}
   $\begin{aligned}
     0.312 & \quad 0.312 & \quad 0.300
    \end{aligned} $
\end{lrbox}

\newsavebox\tonnetzFoote
\begin{lrbox}{\tonnetzFoote}
   $\begin{aligned}
     0.272 & \quad 0.317 & \quad 0.280
    \end{aligned} $
\end{lrbox}

\newsavebox\tonnetzCNMF
\begin{lrbox}{\tonnetzCNMF}
   $\begin{aligned}
     0.212 & \quad 0.306 & \quad 0.237
    \end{aligned} $
\end{lrbox}

\newsavebox\cqtSF
\begin{lrbox}{\cqtSF}
   $\begin{aligned}
     0.311 & \quad \textbf{0.339} & \quad \textbf{0.312}
    \end{aligned} $
\end{lrbox}

\newsavebox\cqtFoote
\begin{lrbox}{\cqtFoote}
   $\begin{aligned}
     \textbf{0.570} & \quad 0.311 & \quad \textbf{0.353}
    \end{aligned} $
\end{lrbox}

\newsavebox\cqtCNMF
\begin{lrbox}{\cqtCNMF}
   $\begin{aligned}
     \textbf{0.296} & \quad \textbf{0.311} & \quad \textbf{0.287}
    \end{aligned} $
\end{lrbox}

%%%%%

\begin{table}
  \centering
  \begin{adjustbox}{width=\textwidth}
  \begin{threeparttable}
    \begin{tabular}{c|l|c|c|c} 
\toprule
     \multicolumn{2}{c|}{\textbf{Training dataset} and \textbf{Feature}}  & \multicolumn{1}{c}{\textbf{SF}} & \multicolumn{1}{c}{\textbf{Foote}} & \multicolumn{1}{c}{\textbf{CNMF}} 
     \\ \midrule 
    \multirow{5}{*}{}&   
         \multirow{1}{*}{MFCC } & \usebox{\mfccSF} & \usebox{\mfccFoote} & \usebox{\mfccCNMF} \\\cline{2-5}
        & \multirow{1}{*}{PCP} & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\cline{2-5}
        & \multirow{1}{*}{Tonnetz} & \usebox{\tonnetzSF} & \usebox{\tonnetzFoote} & \usebox{\tonnetzCNMF} \\\cline{2-5} 
        & \multirow{1}{*}{CQT} & \usebox{\cqtSF} & \usebox{\cqtFoote} & \usebox{\cqtCNMF} \\\cline{1-5} 
    \multirow{1}{*}{GTZAN}& 
        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddioaSF} & \usebox{\embeddioaFoote} & \usebox{\embeddioaCNMF} \\\cline{1-5} 
    \multirow{1}{*}{MSD}& 
        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\\bottomrule
    \end{tabular}
    \caption[Metric comparison for different audio features]{Comparison of precision, recall, and f-measure for different features obtained using the SF, Foote, and CNMF algorithms \cite{sf} \cite{foote} \cite{cnmf} on the SALAMI dataset. Sliding windowed segments across the audio signal input signal is 4 seconds}\label{ta:results}
  \end{threeparttable}
  \end{adjustbox}
\end{table}
